---
title: "exercise 2"
author: "Samuel Orso"
date: "2024-09-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Lecture 7: Object-oriented programming

1. Create a `summary` function for the class `pixel`. Verify the dispatch before and after implementing the summary function.
2. Describe the difference between `t.test()` and `t.data.frame()`. What happens if you run the following code and why?
    ```{r, eval=F}
    x <- structure(1:10, class = "test")
    t(x)
    ```

<ol start="3"> 
<li>Read the documentation for <code class="remark-inline-code">UseMethod()</code> and explain why the following code returns the results that it does.</li></ol>
```{r, eval=F}
g <- function(x) {
  x <- 10
  y <- 10
  UseMethod("g")
}
g.default <- function(x) c(x = x, y = y)

x <- 1
y <- 1
g(y)
```

<ol start="4"><li> What do you expect this code to return? What does it actually return and why?</li></ol>
```{r, eval=F}
generic2 <- function(x) UseMethod("generic2")
generic2.a1 <- function(x) "a1"
generic2.a2 <- function(x) "a2"
generic2.b <- function(x) {
  class(x) <- "a1"
  NextMethod()
}

generic2(structure(list(), class = c("b", "a2")))
```

## Lecture 8: Webscraping
1. Play with [CSS Diner](https://flukeout.github.io/) to get familiar with CSS Selectors.
2. Follow this [workflow](https://smac-group.github.io/ds/section-web-scraping.html#section-workflow). It uses the _SelectorGadget_. Propose an alternative solution using CSS selectors. You will probably need to use the developer tools of your browser.
3. Repeat exercise 2. using `RSelenium` or `chromote`. 
4. Extract the information from the World bank data example using regular expressions. 

## Lecture 9: Shiny applications

1. Develop the app seen in class by adding a second tab with a data table that reports summary statistics of the Old Faithful Geyser (see the UI of the [Buffon's needle example](https://smac-group.github.io/ds/section-shiny-web-applications.html#section-step-2-frontend))

2. Draw the new reactive graph. Can you make the app more efficient? How?

3. Play with different themes using the following code and checkout your console.
```{r,eval=FALSE}
library(shiny)
library(bslib)
thematic::thematic_shiny(font = "auto")

ui <- fluidPage(
  theme = bs_theme(),
  ...
)

server <- function(input, output) {
  bs_themer()
  ...
}

shinyApp(ui, server)
```
