---
title: "Exercice 1"
author: "Samuel Orso"
date: "2024-08-25"
output:
  pdf_document: 
    highlight: monochrome
    includes:
      in_header: "preamble.tex"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Lecture #2: R Markdown

Basic manipulations:   
1. Create a RMarkdown HTML document in `RStudio` and "`knit`" it.
1. Create a new header of type 2.
1. Make a linear regression with "Sepal Length" as a response and 
"Sepal Width" as an explanatory variable from the `iris` dataset and save the result. 
1. Highlight the code with `monochrome` style.
1. Print the summary of the linear regression.
1. Include the QQplot from the linear regression. Change to filled dots.
1. Print the head of the `iris` dataset with `kable`.
1. Remove the `.` from the labels (click [here](https://bookdown.org/yihui/rmarkdown-cookbook/kable.html#change-column-names)).

More advanced manipulations:
1. Install `kableExtra`. And perform the examples shown in the slides with `iris` dataset.
1. Using Mathpix, reproduce equation (6.1) of the paper [https://arxiv.org/abs/math/0303109](https://arxiv.org/abs/math/0303109)
1. Add the Reference and cite it in the RMarkdown.
1. Recreate your RMarkdown into a Quarto document.

## Lecture #3: GitHub
1. Create a GitHub repo for the RMarkdown file (.Rmd) you created in the previous exercise.
1. Edit the README.md file, push the .Rmd.
1. By two. Invite (person A) someone else (person B) to work on your repo and try:
  - Repo is up-to-date. Person B modifies .Rmd and pushes the changes, person A pulls the changes.
  - Repo is up-to-date. Person A modifies 1st section of .Rmd, person B modifies 2nd section (no conflict) of .Rmd. No push, no pull in between. Now person A commits and pushes. Then person B tries to commit and push. Try to solve until repo is up-to-date.
  - Same as last point, but person B modifies 1st section of .Rmd (conflict).
  
## Lecture #4: Data structures
Using the following code:
```{r, eval=F}
set.seed(1)
A <- matrix(rnorm(20), ncol = 2)
B <- matrix(rnorm(20), ncol = 2)
```
1. What are the dimensions of $A$ and $B$? Compute $A^TB$ and $AB^T$.
2. Combine $A$ and $B$ row-wise to create $C$.
3. Let $D$ be a copy of $C$ centered around the mean
columnwise.
The unbiased estimator of the covariance matrix of
$C$ is defined as $$\frac{1}{n-1}D^TD,$$
where $n$ is the number of rows of $D$.
Compute this quantity.
Compare with `cov(C)`.

## Lecture #5: Control Structures
#### Bootstrap
The bootstrap is a well-known method in statistics since Efron's seminal paper in 1979. The bootstrap is easy to implement and straightforward to use. There exist many different schemes for the bootstrap, we present the simplest form:

1.  Compute the statistic on the sample: $\hat{\theta} = g(x_1,\dots,x_n)$.
2.  Create a new sample $x_1^\ast,\dots,x_n^\ast$ by drawing data from the original sample **at random with replacement**. This new sample is called a *bootstrapped sample*.
3.  Compute the statistic on the bootstrapped sample: $\hat{\theta}^\ast = g(x_1^\ast,\dots,x_n^\ast)$.
4.  Repeat 2. and 3. $B$ times.
5.  Compute the unbiased estimator of the variance: $$\frac{1}{B-1}\sum_{b=1}(\hat{\theta}^\ast_{b}-\hat{\theta})^2.$$


1. Load a dataset using `data("ToothGrowth")`. Create 
two vectors of tooth lengths corresponding to
`OJ` and `VC` factors respectively. Compute the
mean of each vector.
2. Create a bootstrap distribution for each vector
using $B=10,000$ and a for loop. Checkout
the `sample` function for sampling at random with replacement.
3. Using `ggplot2`, make a graph of the bootstrap
distributions by plotting two histograms on the same plot. 

## Lecture #6: Functions
* What does the following code return?
```{r, eval=F}
x <- 2
f1 <- function(x) {
  function() {
    x + 3
  }
}
f1(1)()
```

* How would you usually write these codes?
```{r, eval=F}
`+`(1, `*`(2, 3))
`*`(3, `+`(2, 1))
```

* How could you make this function call easier to read?
```{r, eval=F}
mean(, TRUE, x = c(seq(10), rep(NA,3)))
```

* Does the following code throw an error when executed? Why or why not?
```{r, eval=F}
f2 <- function(a, b) {
  a * 3
}
f2(3, stop("This is an error!"))
f2(stop("This is an error!"), 3)
```

* Propose an infix function.